Collaborative Visual Analysis on the Web with RCloud

### 2015-06-26 relatedwork.tex
copy editing

An earlier study by Kandel et al argues that data wrangling
(cleaning, parsing and transformation)is a major part of exploratory
analysis and visualization~\cite{Kandel:2011:RDI}.
% We view this as attacking a different semantic level than ours, but also showing
Although attacking a different semantic level from ours, it shows
the need for an environment that enables better sharing
of the knowledge, tools and processes to do this. Anecdotally
we find much frustration among practitioners that this knowledge
is difficult to find and often is not recorded or available in a
reusable form even within the same organization.

@@

There has been noteworthy work on specific techniques
to support collaborative or social code development and data analysis,
such as social bookmarking \cite{Millen:2006:DSB} \cite{Heer:2007:VAV}
and crowdsourcing \cite{Fast:2014:ECS}.
Similarly, there are computational methods to support high
performance execution in incremental code development
environments \cite{Guo:2010:TPI}.
The goal of RCloud is to define an environment in which many such
techniques may be integrated and made available to a broad community.
\begin{figure*}
\centering
\includegraphics[width=.95\linewidth]{fig/notebook/notebook.pdf}
\caption{\label{fig:notebook}An RCloud notebook is a sequence of
\emph{cells}, each a snippet of source in one of the supported languages (typically R, but Python and others are also supported) or Markdown. The main creation workflow involves editing notebooks, which are transparently stored as git repositories in GitHub, providing us with easy access primitives for version tracking. Notebooks can be executed as they're edited (left), or in a standalone viewer (right), via a slightly different URL. This provides a lightweight, low-friction mechanism for sharing results which we discuss in detail in Section~\ref{sec:interviews}. }
\end{figure*}

One high-level goal is to reduce the gap between implementers and
deployers in visual analytics. The fusion of development with
production operations in software release management (``DevOps''
\cite{Httermann:2012:DD} or ``continuous integration''
\cite{Fowler:2006:Continuous}) is a trend in web services and similar
fields. By making it convenient for data scientists to expend just a
little additional effort when creating experiments, we may be able to
eliminate the need for programming teams to recreate their work to
deploy it in production, which has a high cost in time, expense and
accuracy.

>>>>

An earlier study by Kandel et al argues that data wrangling
(cleaning, parsing and transformation)is a major part of exploratory
analysis and visualization~\cite{Kandel:2011:RDI}.
% We view this as attacking a different semantic level than ours, but also showing
Although attacking a different semantic level from ours, it shows
the need for an environment that enables better sharing
of wrangling knowledge, tools and processes. Anecdotally
we find much frustration among practitioners that this knowledge
is difficult to find and often is not recorded or available in a
reusable form even within the same organization.

@@

There has been noteworthy work on specific techniques
to support collaborative or social code development and data analysis,
such as social bookmarking \cite{Millen:2006:DSB} \cite{Heer:2007:VAV}
and crowdsourcing \cite{Fast:2014:ECS}.
Similarly, there are computational methods to support high
performance execution in incremental code development
environments \cite{Guo:2010:TPI}.
The goal of RCloud is to define an environment in which many such
techniques may be integrated and made available to a broad community.
\begin{figure*}
\centering
\includegraphics[width=.95\linewidth]{fig/notebook/notebook.pdf}
\caption{\label{fig:notebook}An RCloud notebook is a sequence of
\emph{cells}, each a snippet of source in one of the supported languages (typically R, but Python and others are also supported) or Markdown. The main creation workflow involves editing notebooks, which are transparently stored as git repositories in GitHub, providing us with easy access to primitives for version tracking. Notebooks can be executed as they're edited (left), or in a standalone viewer (right), via a slightly different URL. This provides a lightweight, low-friction mechanism for sharing results which we discuss in detail in Section~\ref{sec:interviews}. }
\end{figure*}

One high-level goal is to reduce the gap between implementers and
deployers in visual analytics. The fusion of development with
production operations in software release management (``DevOps''
\cite{Httermann:2012:DD} or ``continuous integration''
\cite{Fowler:2006:Continuous}) is a trend in web services and similar
fields.
%% By making it convenient for data scientists to expend just a
%% little additional effort when creating experiments, we may be able to
%% eliminate the need for programming teams to recreate their work to
%% deploy it in production, which has a high cost in time, expense and
%% accuracy.
%gw{sentence was just too long}
When programming teams recreate the work of data scientists to
deploy it in production, it has a high cost in time, expense and
accuracy. By making it convenient for data scientists to productionize
their experiments, we may be able to eliminate the need for this costly step.
